Combining parsing with sentence understanding

### 2016-03-10 writing/hard_stack_paper/paper.tex
Abstract update.

\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\item TreeRNNs are great, don't work for big data.
\item We present the transition-based TreeRNN implementation -- makes efficient training possible, show that it helps relative to seq models.
\item Further, attention has proven powerful for extending sequence models. We introduce constituent-by-constituent attention, and find it to be effective here, too.
\end{itemize}
\end{abstract}

\todo{Anonymize.}
\todo{Name the damn model!}

>>>>

\begin{document}
\maketitle
\begin{abstract}

Tree-structured neural networks are highly as effective sentence models, but they can only operate on parsed sentences, and do not support batched computation, making them prohibitively slow for large-scale tasks. This paper presents the parser-interpreter neural network, which reimplements a tree-structured network within a transition-based neural constituency parser. This allows us to address both weaknesses: the transition-based architecture of the parser makes it possible to perform tree-structured interpretation in an efficient batched setting, and the integrated parser allows the model to interpret unparsed data with nearly no loss in accuracy. In addition, our model supports a novel and effective method for handling local context in sentence interpretation and integrates will with soft attention methods for sentence pair tasks.

\end{abstract}

\todo{Anonymize.}

\todo{Fill in name where needed.}

\todo{SST!}

\todo{Model 1!}
